\cvsection{Additional Experience}
\begin{cventries}
  \cventry
    {Cycle Courier}
    {Deliveroo}
    {Brighton}
    {Jun. 2016 - Present}
    {
      \begin{cvitems}
        \item {Working in all weathers to deliver food in physically demanding geography of Brighton.}
        \item {Dealing with range of temperaments of customers and restaurants.}
        \item{Personally managing time as a self-employed worker.}
      \end{cvitems}
    }
  \cventry
    {International Summer School}
    {Hong Kong University of Science \& Technology}
    {Hong Kong}
    {Summer 2015}
    {
      \begin{cvitems}
        \item {Studied Electro-robot Design, learning to design and build a robot from elementary components that could sense and navigate itself around a course. Our team won the award for best robot.}
        \item {Studied Business Statistics, improving my ability to handle statistics in real-world applications.}
        \item {Worked with students from around the world and lived and studied in a very different culture.}
      \end{cvitems}
    }
  \cventry
    {Sales Advisor}
    {Domestic \& General}
    {Brighton}
    {Dec. 2012 - Dec. 2013}
    {
      \begin{cvitems}
        \item {Worked in target-based sales telesales selling insurance products.}
        \item{Further developed my communication and compromising skills, building rapport with customers to reassure their concerns.}
        \item {Worked under pressure to fulfil targets by deadlines whilst remaining calm to be regularly amongst the top-performers.}
      \end{cvitems}
    }
  \cventry
    {Sales Advisor}
    {Pell \& Bales}
    {Brighton}
    {Dec. 2011 - Jun. 2012}
    {
      \begin{cvitems}
        \item {Worked in target-based  telefundraising, raising donations for range of charities.}
        \item{Worked to communicate the aims of the charities and build rapport with donors.}
        \item {Under flexitime arrangement was responsible for managing my own time.}
      \end{cvitems}
    }
\end{cventries}
